---
title: "Solutions for Homework 1"
author: "Jiajun Tao"
date: 2022-09-15
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

Load the `penguins` dataset first.

```{r}
data("penguins", package = "palmerpenguins")
```

Then, let's describe the dataset!

Here's the summary of the dataset.

```{r}
summary(penguins)
```

I think `species`, `island` are important qualitative variables, and `flipper_length_mm`, `body_mass_g` are important quantitative variables.

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r round(mean(penguins$flipper_length_mm,na.rm = TRUE),2)` mm.

Make a scatterplot of `flipper_length_mm`(y) vs `bill_length_mm`(x).

```{r, warning = FALSE}
ggplot(data = penguins,
       aes(x = bill_length_mm,
           y = flipper_length_mm)) + 
  geom_point(aes(color = species,
                 shape = species))
```

Export my scatterplot.

```{r, warning = FALSE, message = FALSE}
ggsave("p8105_hw1_jt3386_scatterplot.pdf")
```

# Problem 2

First create a data frame.

```{r}
pb2_df = 
  tibble(
    rdm_sample = rnorm(10),
    rdm_sample_pos = rdm_sample > 0,
    chr_sample = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
    fct_sample = factor(x = c(1, 3, 2, 1, 1, 3, 2, 2, 1, 3),
                        labels = c("One", "Two", "Three"))
  )
pb2_df
```

Take the mean of each variable.

```{r, warning = FALSE}
mean(pull(pb2_df,rdm_sample))
mean(pull(pb2_df,rdm_sample_pos))
mean(pull(pb2_df,chr_sample))
mean(pull(pb2_df,fct_sample))
```

The double variables and the logical variables work, however, the character variables and the factor variables don't work.

Apply the `as.numeric` function to the logical, character, and factor vector.

```{r, eval = FALSE}
as.numeric(pull(pb2_df,rdm_sample_pos))
as.numeric(pull(pb2_df,chr_sample))
as.numeric(pull(pb2_df,fct_sample))
```

The logical variables are converted to 0 or 1. If the value is TRUE, it will be converted to 1. And if the value is FALSE, it will be converted to 0.

The character variables can not be converted to numeric variables.

The factor variables can be converted to numeric variables and the numeric codes corresponding to the factor levels will be returned.

This could help explain that I can take the mean of logical variables because they are just converted to numeric variables, but that could not help explain why I cannot take the mean of factor variables.